Centralized Programming for Distributed Control Planes

### 2016-01-28 paper/evaluation.tex
updating experiments
shrinking images

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/compilation-times-dc.png}
\label{fig:compilation-times-dc}
\caption{Data center compilation times.}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/compilation-times-backbone.png}
\label{fig:compilation-times-dc}
\caption{Data center compilation times.}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/config-compression-dc.png}
\label{fig:compilation-compression-dc}
\caption{Data center config minimization.}
\end{figure}

>>>>

\begin{figure}[t!]
  \centering
  \begin{minipage}[b]{0.45\linewidth}
    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-dc.png}
  \end{minipage}
  \quad
  \begin{minipage}[b]{0.45\linewidth}
    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-backbone.png}
  \end{minipage}
  \caption{Compilation times.}
  \label{fig:compilation-times}
\end{figure}

\begin{figure}[t!]
  \centering
  \begin{minipage}[b]{0.45\linewidth}
    \includegraphics[width=1.1\columnwidth]{figures/config-compression-dc.png}
  \end{minipage}
  \quad
  \begin{minipage}[b]{0.45\linewidth}
    \includegraphics[width=1.1\columnwidth]{figures/config-compression-backbone.png}
  \end{minipage}
  \caption{Configuration minimization.}
  \label{fig:minipage2}
\end{figure}
